---
title: Bushfire Prone Land
subtitle: Australia wide
format:
  360-analysis-html: default
author: Dean Marchiori
date: last-modified
code-fold: true
---

Load required packages
```{r}
source(here::here("analysis/BFP/R/001_packages.R"))
```

The raw data for this project exists in `data/raw` see `data/README.md` for details.  

This script unzips each state's individual spatial files and caches them in `data/staging`
```{r}
source(here::here("analysis/BFP/R/002_unzip_raw.R"))
```

The following scrips read in the state by state data, and intersect it with the ABS suburbs shapefile. 

WARNING: This takes *many* hours to run. Evaluation of this chunk is suppressed. 

```{r}
#| eval: false

source(here::here("analysis/BFP/R/100_process_suburbs.R"))
source(here::here("analysis/BFP/R/101_process_act.R"))
source(here::here("analysis/BFP/R/102_process_nt.R"))
source(here::here("analysis/BFP/R/103_process_wa.R"))
source(here::here("analysis/BFP/R/104_process_vic.R"))
source(here::here("analysis/BFP/R/105_process_nsw.R"))
source(here::here("analysis/BFP/R/106_process_qld.R"))
source(here::here("analysis/BFP/R/107_process_sa.R"))
source(here::here("analysis/BFP/R/108_process_tas.R"))

```

Combining these into an Australia wide suburb level dataset

```{r}
source(here::here("analysis/BFP/R/200_make_australia.R"))
```